RIScatter: Unifying Backscatter Communication and Reconfigurable Intelligent Surface From a Distribution Perspective

### 2022-11-26 assets/illustration/input_distribution.tex
:dizzy: Manuscript 221103
:lipstick: Update illustrations

\begin{tikzpicture}
	\begin{groupplot}
		[group style={
					rows=3,
					group name=plots,
					x descriptions at=edge bottom,
					y descriptions at=edge left,
					vertical sep=10
				},
			ybar,
			xmin=0,
			xmax=4,
			xtick={1,2,3,4},
			ymin=0,
			ymax=1,
			xlabel={Reflection State},
			enlarge x limits={value=0.25,upper},
			enlarge y limits={value=0.1,upper},
			width=10cm,
			height=2.6cm,
			every axis plot/.append style={bar shift=0}
		]
		\nextgroupplot
		\addplot[blue,fill=blue!30!white] coordinates {(-1,-1)};
		\addplot[blue,fill=blue!30!white,postaction={pattern=horizontal lines},pattern color=.] coordinates {(1,0.25)};
		\addplot[blue,fill=blue!30!white,postaction={pattern=north west lines},pattern color=.] coordinates {(2,0.25)};
		\addplot[blue,fill=blue!30!white,postaction={pattern=vertical lines},pattern color=.] coordinates {(3,0.25)};
		\addplot[blue,fill=blue!30!white,postaction={pattern=north east lines},pattern color=.] coordinates {(4,0.25)};
		\legend{BackCom/AmBC/SR}
		\nextgroupplot[ylabel={Probability Distribution}]
		\addplot[red,fill=red!30!white] coordinates {(-1,-1)};
		\addplot[red,fill=red!30!white,postaction={pattern=horizontal lines},pattern color=.] coordinates {(1,0)};
		\addplot[red,fill=red!30!white,postaction={pattern=north west lines},pattern color=.] coordinates {(2,1)};
		\addplot[red,fill=red!30!white,postaction={pattern=vertical lines},pattern color=.] coordinates {(3,0)};
		\addplot[red,fill=red!30!white,postaction={pattern=north east lines},pattern color=.] coordinates {(4,0)};
		\legend{RIS}
		\nextgroupplot
		\addplot[brown,fill=brown!30!white] coordinates {(-1,-1)};
		\addplot[brown,fill=brown!30!white,postaction={pattern=horizontal lines},pattern color=.] coordinates {(1,0.125)};
		\addplot[brown,fill=brown!30!white,postaction={pattern=north west lines},pattern color=.] coordinates {(2,0.625)};
		\addplot[brown,fill=brown!30!white,postaction={pattern=vertical lines},pattern color=.] coordinates {(3,0.25)};
		\addplot[brown,fill=brown!30!white,postaction={pattern=north east lines},pattern color=.] coordinates {(4,0)};
		\legend{RIScatter}
	\end{groupplot}
\end{tikzpicture}

>>>>

\begin{tikzpicture}
	\begin{groupplot}
		[group style={
					rows=3,
					group name=plots,
					x descriptions at=edge bottom,
					y descriptions at=edge left,
					vertical sep=10
				},
			ybar,
			xmin=0,
			xmax=4,
			xtick={1,2,3,4},
			ymin=0,
			ymax=1,
			xlabel={Reflection State},
			enlarge x limits={value=0.25,upper},
			enlarge y limits={value=0.1,upper},
			width=10cm,
			height=2.6cm,
			every axis plot/.append style={bar shift=0}
		]
		\nextgroupplot
		\addplot[blue,fill=blue!30!white] coordinates {(-1,-1)};
		\addplot[blue,fill=blue!30!white,postaction={pattern=north west lines},pattern color=.] coordinates {(1,0.25)};
		\addplot[blue,fill=blue!30!white,postaction={pattern=north east lines},pattern color=.] coordinates {(2,0.25)};
		\addplot[blue,fill=blue!30!white,postaction={pattern=vertical lines},pattern color=.] coordinates {(3,0.25)};
		\addplot[blue,fill=blue!30!white,postaction={pattern=horizontal lines},pattern color=.] coordinates {(4,0.25)};
		\legend{BackCom}
		\nextgroupplot[ylabel={Probability Distribution}]
		\addplot[red,fill=red!30!white] coordinates {(-1,-1)};
		\addplot[red,fill=red!30!white,postaction={pattern=north west lines},pattern color=.] coordinates {(1,0)};
		\addplot[red,fill=red!30!white,postaction={pattern=north east lines},pattern color=.] coordinates {(2,1)};
		\addplot[red,fill=red!30!white,postaction={pattern=vertical lines},pattern color=.] coordinates {(3,0)};
		\addplot[red,fill=red!30!white,postaction={pattern=horizontal lines},pattern color=.] coordinates {(4,0)};
		\legend{RIS}
		\nextgroupplot
		\addplot[brown,fill=brown!30!white] coordinates {(-1,-1)};
		\addplot[brown,fill=brown!30!white,postaction={pattern=north west lines},pattern color=.] coordinates {(1,0.125)};
		\addplot[brown,fill=brown!30!white,postaction={pattern=north east lines},pattern color=.] coordinates {(2,0.625)};
		\addplot[brown,fill=brown!30!white,postaction={pattern=vertical lines},pattern color=.] coordinates {(3,0.25)};
		\addplot[brown,fill=brown!30!white,postaction={pattern=horizontal lines},pattern color=.] coordinates {(4,0)};
		\legend{RIScatter}
	\end{groupplot}
\end{tikzpicture}

### 2022-11-26 assets/illustration/time_structure.tex
:dizzy: Manuscript 221103
:lipstick: Update illustrations

\begin{tikzpicture}[font=\large]
	% BC/AmBC/SR
	\foreach \x in {0,...,3}{
			\draw[blue,fill=blue!30!white,postaction={pattern=horizontal lines},pattern color=.] (0.5*\x,3) rectangle ++(0.5,0.25);
		}
	\foreach \x in {4,...,7}{
			\draw[blue,fill=blue!30!white,postaction={pattern=north west lines},pattern color=.] (0.5*\x,3) rectangle ++(0.5,0.25);
		}
	\foreach \x in {8,...,11}{
			\draw[blue,fill=blue!30!white,postaction={pattern=vertical lines},pattern color=.] (0.5*\x,3) rectangle ++(0.5,0.25);
		}
	\foreach \x in {12,...,15}{
			\draw[blue,fill=blue!30!white,postaction={pattern=north east lines},pattern color=.] (0.5*\x,3) rectangle ++(0.5,0.25);
		}

	% RIS
	\foreach \x in {0,...,15}{
			\draw[red,fill=red!30!white,postaction={pattern=north west lines},pattern color=.] (0.5*\x,2) rectangle ++(0.5,0.25);
		}

	% RIScatter
	\foreach \x in {0,...,1}{
			\draw[brown,fill=brown!30!white,postaction={pattern=horizontal lines},pattern color=.] (0.5*\x,1) rectangle ++(0.5,0.25);
		}
	\foreach \x in {2,...,7}{
			\draw[brown,fill=brown!30!white,postaction={pattern=north west lines},pattern color=.] (0.5*\x,1) rectangle ++(0.5,0.25);
		}
	\foreach \x in {8,...,11}{
			\draw[brown,fill=brown!30!white,postaction={pattern=vertical lines},pattern color=.] (0.5*\x,1) rectangle ++(0.5,0.25);
		}
	\foreach \x in {12,...,15}{
			\draw[brown,fill=brown!30!white,postaction={pattern=north west lines},pattern color=.] (0.5*\x,1) rectangle ++(0.5,0.25);
		}

@@

	\node at (-2,3.125) {BackCom/AmBC/SR};
	\node at (-2,2.125) {RIS};
	\node at (-2,1.125) {RIScatter};

	\draw [pattern=horizontal lines](0.15,0) rectangle ++(0.5,0.25) node[xshift=20,yshift=-3.5] {State 1};
	\draw [pattern=north west lines](2.15,0) rectangle ++(0.5,0.25) node[xshift=20,yshift=-3.5] {State 2};
	\draw [pattern=vertical lines](4.15,0) rectangle ++(0.5,0.25) node[xshift=20,yshift=-3.5] {State 3};
	\draw [pattern=north east lines](6.15,0) rectangle ++(0.5,0.25) node[xshift=20,yshift=-3.5] {State 4};
\end{tikzpicture}

>>>>

\begin{tikzpicture}[font=\large]
	% BC/AmBC/SR
	\foreach \x in {0,...,3}{
			\draw[blue,fill=blue!30!white,postaction={pattern=north west lines},pattern color=.] (0.5*\x,3) rectangle ++(0.5,0.25);
		}
	\foreach \x in {4,...,7}{
			\draw[blue,fill=blue!30!white,postaction={pattern=north east lines},pattern color=.] (0.5*\x,3) rectangle ++(0.5,0.25);
		}
	\foreach \x in {8,...,11}{
			\draw[blue,fill=blue!30!white,postaction={pattern=vertical lines},pattern color=.] (0.5*\x,3) rectangle ++(0.5,0.25);
		}
	\foreach \x in {12,...,15}{
			\draw[blue,fill=blue!30!white,postaction={pattern=horizontal lines},pattern color=.] (0.5*\x,3) rectangle ++(0.5,0.25);
		}

	% RIS
	\foreach \x in {0,...,15}{
			\draw[red,fill=red!30!white,postaction={pattern=north east lines},pattern color=.] (0.5*\x,2) rectangle ++(0.5,0.25);
		}

	% RIScatter
	\foreach \x in {0,...,1}{
			\draw[brown,fill=brown!30!white,postaction={pattern=north west lines},pattern color=.] (0.5*\x,1) rectangle ++(0.5,0.25);
		}
	\foreach \x in {2,...,7}{
			\draw[brown,fill=brown!30!white,postaction={pattern=north east lines},pattern color=.] (0.5*\x,1) rectangle ++(0.5,0.25);
		}
	\foreach \x in {8,...,11}{
			\draw[brown,fill=brown!30!white,postaction={pattern=vertical lines},pattern color=.] (0.5*\x,1) rectangle ++(0.5,0.25);
		}
	\foreach \x in {12,...,15}{
			\draw[brown,fill=brown!30!white,postaction={pattern=north east lines},pattern color=.] (0.5*\x,1) rectangle ++(0.5,0.25);
		}

@@

	\node at (-2,3.125) {BackCom};
	\node at (-2,2.125) {RIS};
	\node at (-2,1.125) {RIScatter};

	\draw [pattern=north west lines](0.15,0) rectangle ++(0.5,0.25) node[xshift=20,yshift=-3.5] {State 1};
	\draw [pattern=north east lines](2.15,0) rectangle ++(0.5,0.25) node[xshift=20,yshift=-3.5] {State 2};
	\draw [pattern=vertical lines](4.15,0) rectangle ++(0.5,0.25) node[xshift=20,yshift=-3.5] {State 3};
	\draw [pattern=horizontal lines](6.15,0) rectangle ++(0.5,0.25) node[xshift=20,yshift=-3.5] {State 4};
\end{tikzpicture}
